Supplementary information

### 2021-09-28 _targets.Rmd
update repro and options

```{targets globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
library(purrr)
library(here)
library(tibble)
library(tarchetypes)
functions <- list.files(here("R"), full.names = TRUE)
walk(functions, source)
tar_option_set(
  packages = c("tibble", "tidyr", "dplyr", "scoringutils", "ggplot2", "purrr",
               "readr"),
  error = "workspace"
)
```

@@

```{targets toy_globals, tar_globals = TRUE}
toy_growth_rates <- tibble(r = c(0, 0.01, 0.1, -0.01, -0.1))
```

@@

```{targets toy_scenarios, tar_simple = TRUE}
expand_grid(
  init = c(100),
  r = toy_growth_rates$r,
  r_error = c(0, 0.01, 0.025, 0.05, 0.1, -0.01, -0.025, -0.05, -0.1),
  additive_error = c(0, 1, 10, -1, -10)
) |> 
  mutate(id = 1:n())
```

@@

- Repeat the scoring process but on the log scale.

```{targets, toy_log_scores, tar_simple = TRUE}
toy_forecasts |>
  mutate(across(.cols = c("true_value", "prediction"), ~ log(.x))) |>
  eval_forecasts(
    summarise_by = c("init", "r", "r_error", "additive_error", "time"),
    metrics = c("crps")
  )
```

@@

If all`{targets}` were run in non-interactive mode, then the pipeline is ready to run using the following,

@@

>>>>

```{targets globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
library(purrr)
library(here)
library(tibble)
library(tarchetypes)
functions <- list.files(here("R"), full.names = TRUE)
walk(functions, source)
tar_option_set(
  packages = c("tibble", "tidyr", "dplyr", "scoringutils", "ggplot2", "purrr",
               "readr"),
  error = "continue"
)
```

@@

```{targets toy_globals, tar_globals = TRUE}
toy_growth_rates <- tibble(r = c(0, 0.1, 0.5, -0.1, -0.5))
```

@@

```{targets toy_scenarios, tar_simple = TRUE}
expand_grid(
  init = c(100),
  r = toy_growth_rates$r,
  r_error = c(0, 0.01, 0.05, 0.1, 0.25, -0.01, -0.05, -0.1, -0.25),
  additive_error = c(0, 5, 10, -5, -10)
) |> 
  mutate(id = 1:n())
```

@@

- Repeat the scoring process but on the log scale. Here we have to pad by a small number as cannot take the log of zero.

```{targets, toy_log_scores, tar_simple = TRUE}
toy_forecasts |>
  mutate(across(.cols = c("true_value", "prediction"), ~ log(.x + 0.001))) |>
  eval_forecasts(
    summarise_by = c("init", "r", "r_error", "additive_error", "time"),
    metrics = c("crps")
  )
```

@@

The pipeline can be regenerated by rendering this file,

```{r, eval = FALSE}
rmarkdown::render("_targets.Rmd")
```

Thee pipeline can then be run using,

@@

The pipeline can be regenerated and run using the following single step

```{bash, eval = FALSE}
. _targets.sh
```
